\newpage
\thispagestyle{empty}

\singlespacing
{\large\bf About Technicolor.\\}

Technicolor, a worldwide technology leader in the media and entertainment sector, is at the forefront of digital innovation. Our world class research and innovation laboratories and our creative talent pool enable us to lead the market in delivering advanced services to content creators and distributors. We also benefit from an extensive intellectual property portfolio focused on imaging and sound technologies, supporting our thriving licensing business. \\

{\large\bf About Technicolor Rennes – A pole of excellence in creation, distribution and content access technologies. \\}

Technicolor Rennes is the largest technology centre of Technicolor Group. Pole of excellence in the whole image chain, the Rennes centre is the supplier of innovative solutions for Media \& Entertainment Industries. A part of the activities is focused on the compression, protection, transmission, production and management of high definition contents while other technological solutions are developed to respond to the demands of network operators and to meet the needs of Media \& Entertainment customers.
Technicolor Rennes has built partnerships with top academic institutes in Europe, public institutes, industrial partners and is involved in all French and European research programs such as RNRT, RNTL, RIAM, MEDEA, ITEA, IST, CNES, ESA ... \\

{\large\bf Research and Development themes addressing Technicolor Group strategy. \\}

\begin{itemize}
  \item Compression/Decompression with audio/video processing
  \item Signal and image acquisition and processing
  \item Mobile and broadband technology
  \item Content security on the whole image chain
  \item 3D
  \item Licensing
  \item Digital decoder platforms including the most recent technologies such as Personal Video Recorder, MPEG4 coding, video over Internet Protocol, high definition. \\
\end{itemize}

{\large\bf Activities.}

Technicolor's activities are organized into three operating divisions:
\begin{description}
  \item[Technology] Research \& Innovation, Licensing, Media Navi.
  \item[Connected Home] Formerly Digital Delivery.
  \item[Entertainment Services] Creative Services (Visual effects, animation \& post production services), DVD services, IZ-ON Media (provide digital place-based media services).  \\
\end{description}

\doublespacing