\begin{thebibliography}{99}

\bibitem{c1}
J. Malik and X. Ren, Learning a classification model for segmentation, {\it Computer Vision, International Conference}, 2003.

\bibitem{c2}
S. Boltz; F. Nielsen and S. Soatto, Earth mover distance on superpixels, {\it International Conference on Image Processing}, 2010.

\bibitem{c3}
E. Boros; P. Hammer and G. Tavares, Preprocessing of unconstrained quadratic binary optimization, {\it RUTCOR}, 2010

\bibitem{c4}
E. Boros and P. Hammer, Pseudo-boolean optimization, {\it Discrete applied Mathematics.}, 2002

\bibitem{c5}
B. Horn and B. Schunck, Determining Optical Flow, {\it Artificial Intelligence}, 1981

\bibitem{c6}
H. Ishikawa and P. Bouthemy, Multimodal estimation of discontinous optical flow using Markov random fields, {\it TPAMI.}, 1993

\bibitem{c7}
V. Lempitsky, S. Roth and C. Rother, Fusion Flow: Discrete-Continuos optimization for optical flow estimation, {\it Computer Vision and Pattern Recognition}, 2008

\bibitem{c8}
M. Reso and J. Jachalsky, Temporally Consistent Superpixels, {\it International Conference Computer Vision.}, 2011

\bibitem{c9}
R. Achanta; A. Shaji; K. Smith; Aurelien Lucchi; P. Fua and S. Susstrunk SLIC, Superpixels compared to state of the art superpixel methods, {\it Discrete applied Mathematics.}, 2002

\bibitem{c10}
F. Perbet and A. Maki, Homogeneus superpixels from random walks, {\it MVA.}, 2011

\bibitem{c11}
C. Xu and J.J. Corso. Evaluation of super-voxel methods for early video proccesing, {\it Computer Vision and Pattern Recognition}. 2012.

\bibitem{c12}
A. Shekhovtsov, I. Kovtun and V. Hlavac. Efficient MRF deformation model for non-rigid image matching, {\it Computer Vision and Pattern Recognition}. 2007.

\bibitem{c13}
J. Sun, N.N Shen and H.Y. Shum. Stereo matching using propagation belief, {\it TPAMI}. 2003.

\bibitem{c14}
C. Rother, V. Kolmogorov and A. Blake. Grabcut: Interactive foreground extraction using iterated graph cuts, {\it SIGGRAPH}. 2004.

\bibitem{c15}
L. Yang, Y. Guo, X. Wu and X. Wang. A new video segmentation approach: Grabcut in local window,  {\it Soft Computing and Pattern Recognition}. 2011.

\bibitem{c16}
Y. Wu, J. Lim and M.-H. Yang. Online object tracking: A benchmark, {\it Computer Vision and Pattern Recognition}. 2013.

\bibitem{c17}
S. Baker, D. Scharstein, J.P. Lewis, S. Roth, M.J. Black and R. Szeliski. A Database and Evaluation Methodology for Optical Flow, {\it International Journal Computer Vision}. 2013.

\bibitem{c18}
Y. Boykov, M-P. Jolly. Interactive Graph Cuts for Optimal Boundary \& Region Segmentation of Objects in N-D images, {\it International Conference on Computer Vision}. 2013.

\bibitem{c19}
W. Li, D. Cosker and M. Brown. An anchor patch based optimization framework for reducing optical flow drift in long image sequences, {\it Asian Conference on Computer Vision}. 2012.

\bibitem{c20}
T. Crivelli, P.-H. Conze, P. Robert, M. Fradet and P. Perez. Multi-step flow fusion: towards accurate and dense correpondence in long video shots, {\it British Conference Machine Vision}. 2012.

\bibitem{c21}
M. Tao, J. Bai, P. Kohli, and S. Paris. SimpleFlow: A Non-iterative, Sublinear Optical Flow Algorithm, {\it Computer Graphics Forum, Eurographics}. 2012.

\bibitem{c22}
T.B. Dinh, N. Vo, and G. Medioni. Context tracker: Exploring Suporters and Distracters in Unconstrained Environments. {\it Computer Vision and Pattern Recognition }. 2011.

\bibitem{c23}
S. Hare, A. Saffari, and P.H.S. Torr, Struck: Structured Output Tracking with Kernels.  {\it International Conference on Computer Vision}. 2011.

\bibitem{c24}
X. Jia, H. Lu, and M.H. Yang. Visual Tracking via Adaptive Structural Local Sparse Appearance Model. {\it Computer Vision and Pattern Recognition }. 2012.

\bibitem{c25}
B. Babenko, M.H. Yang, and S. Belongie. Visual Tracking with Online Multiple Instance Learning. {\it Computer Vision and Pattern Recognition}. 2009.

\bibitem{c26}
Z. Kalal, J. Matas, and K.Mikolajczyk. P-N Learning: Bootstrapping Binary Classiﬁers by Structural Constraints. {\it Computer Vision and Pattern Recognition}. 2010.

\bibitem{c27}
D.J. Butler,  J. Wulff,  G.B. Stanley, and M.J. Black. A naturalistic open source movie for optical flow evaluation.{\it European Conference in Computer Vision}. 2012.

\bibitem{c28}
G. Farneback. Two-Frame Motion Estimation Based on Polynomial Expansion. {\it Scandinavian Conference, SCIA }. 2003.

\bibitem{c29}
Brox, A. Bruhn, N. Papenberg, J. Weickert. High accuracy optical flow estimation based on a theory for warping. {\it European Conference in Computer Vision}. 2004.

\bibitem{c30}
Berthold K.P. Horn and Brian G. Schunck. Determining Optical Flow. {\it Artificial Intelligence }. 1981.

\bibitem{c31}
Lucas, B., and Kanade, T. An Iterative Image Registration Technique with an Application to Stereo Vision, {\it International Joint Conference on Artificial Intelligence }. 1981.

\bibitem{c32}
Zach, T. Pock and H. Bischof. A Duality Based Approach for Realtime TV-L1 Optical Flow, {\it Proceedings of Pattern Recognition (DAGM) }. 2007.

\bibitem{c33}
T. Brox and J. Malik. Object Segmentation by Long Term Analysis of Point Trajectories, {\it European Conference in Computer Vision}. 2010.

\bibitem{c34}
P. Ochs and T. Brox. Object Segmentation in Video: A Hierarchical Variational Approach for Turning Point Trajectories into Dense Regions, {\it International Conference in Computer Vision }. 2011.

\bibitem{c35}
A. Bugeau and P. Perez. Detection and segmentation of moving objects in highly dynamic scenes, {\it Computer Vision and Pattern Recognition }. 2007.

\bibitem{c36}
S.M. Smith. ASSET-2: Real-Time Motion Segmentation and Shape Tracking. {\it Computer Vision}. 1995. 

\bibitem{c37}
Carlo Tomasi and Takeo Kanade. Detection and Tracking of Point Features. {\it Carnegie Mellon University Technical Report CMU-CS-91-132 }, 1991.

\bibitem{c38}
A. Hilsmann and P. Eisert. Deformable Object Tracking Using Optical Flow Constraints. {\it European Conference in Visual Media Production }, 2007.

\bibitem{c39}
H-S. Chang and Y-C. Frank Wang. Superpixel-Based Large Displacement Optical Flow. {\it International Conference on Image Processing }, 2013.

\bibitem{c40}
D. Sun, S. Roth J.P. Lewis, and M.J. Black. Learning Optical Flow. {\it European Conference on Computer Vision }, 2008.

\bibitem{c41}
A. Rav-Acha, P. Kohli, C. Rother and A. Fitzgibbon. Unwrap Mosaics: A new representation for video editing. {\it ACM SIGGRAPH}, 2008. 

\bibitem{c42}
C. Wu. Towards Linear-time Incremental Structure from Motion. {\it International Conference on 3D Vision}, 2013.

\bibitem{c43}
M. Zucchelli. Optical Flow Based Structure From Motion. {\it Doctoral Dissertation for the Royal Institute of Technology, Stockholm}, 2002

\bibitem{c44}
Y. Cheng. Mean Shift, Mode Seeking, and Clustering, {\it IEEE Transactions on Pattern Analysis and Machine Intelligence (TPAMI)}, 1995.

\bibitem{c45}
Gary Bradski and Adrian Kaehler: Learning OpenCV: Computer Vision with the OpenCV Library. {\it  O'Reilly Media}, 2008.

\bibitem{c46}
S. Rangarajan and S.T. Birchfield. Spatiograms versus histograms for region-based tracking. {\it Computer Vision and Pattern Recognition}, 2005.

\bibitem{c47}
H. Grabner, M. Grabner, and H. Bischof. Real-time Tracking via On-line Boosting. {\it British Machine Vision Conference}. 2006.

\bibitem{c48}
Z. Kalal, K. Mikolajczyk, and J. Matas. Tracking-Learning-Detection. {\it Pattern Analysis and Machine Intelligence}. 2011.

\bibitem{c49}
F.L. Bookstein. Principal Warps: Thin-Plate Splines and the Decomposition of Deformations. {\it Pattern Analysis and Machine Intelligence}. 1989.


\end{thebibliography}
