\chapter{Conclusions} \label{chap:conclusion}

A framework to combine tracking and optical flow methods to improve 
object based dense motion description is presented. The pipeline is 
composed of three main steps, object tracking, segmentation and 
flow estimation. For the segmentation step a new promising video object 
segmentation algorithm was proposed, and, to the best of our knowledge, 
the introduced superpixel flow is the first energy based algorithm for superpixel matching.
This superpixel matching technique is used to track regions that belong to the background of the 
scene and allows a fine initialization of segmentation techniques, leading to a precise and stable 
segmentation method for objects in video sequences.
For the last step, a flow estimation method based on a modification of the simple-flow method to use 
the obtained segmentation mask is presented. The experiments showed that this object based flow estimation improves the dense motion 
estimation in comparison to optical flow techniques. Moreover, it is also shown than a simple 
mixing of tracking and locally computed optical flow is already better than global optical flow methods. 
This mixture seems to be in contradiction with the classic aperture problem. However, as the results are evaluated only inside an interest region (the object), this problem disappears. Thus, as the tracker provides 
a global motion displacement, and the dense flow is only computed within the given tracker windows, a 
more precise flow is obtained.
Future work can be further explored in the use of the object flow as feedback hint for tracking-by-detection methods. Also, 
several kind of applications of the object flow can be more deeply approached. For instance, 
in the structure-from-motion pipeline, video based rendering, automatic video edition, and video in-painting  among others.



%A method for superpixel matching in a flow-like
%behavior had been presented. We may call it superpixel propagation, or super-pixel flow. This
%technique shows robustness in the labeling of the
%matches, and seems to be able to improve the results
%for object segmentation in video sequences when
%using the Grab-cut algorithm. Another motivation for
%this technique, however may be as initialization of
%optical flow techniques, to obtain more robust results
%due to a good initial guess for energy minimization
%methods. This has to be looked at more deeply in future work.