\begin{thebibliography}{99}

\bibitem{c12}
A. Shekhovtsov, I. Kovtun and V. Hlavac. Efficient MRF deformation model for non-rigid image matching, {\it Computer Vision and Pattern Recognition}. 2007.

\bibitem{c24}
B. Babenko, M.H. Yang, and S. Belongie. Visual Tracking with Online Multiple Instance Learning. {\it Computer Vision and Pattern Recognition}. 2009.

\bibitem{c5}
B. Horn and B. Schunck, Determining Optical Flow, {\it Artificial Intelligence}, 1981.

\bibitem{c22}
Brox, A. Bruhn, N. Papenberg, J. Weickert. High accuracy optical flow estimation based on a theory for warping. {\it European Conference in Computer Vision}. 2004.

\bibitem{c14}
C. Rother, V. Kolmogorov and A. Blake. Grabcut: Interactive foreground extraction using iterated graph cuts, {\it SIGGRAPH}. 2004.

\bibitem{c3}
E. Boros; P. Hammer and G. Tavares, Preprocessing of unconstrained quadratic binary optimization, {\it RUTCOR}, 2010.

\bibitem{c4}
E. Boros and P. Hammer, Pseudo-boolean optimization, {\it Discrete applied Mathematics.}, 2002.

\bibitem{c10}
F. Perbet and A. Maki, Homogeneus superpixels from random walks, {\it MVA.}, 2011.

\bibitem{c25}
J. Shi and C. Tomasi. Good features to track. {\it Conference on Computer Vision and Pattern Recognition }, 1994. 

\bibitem{c13}
J. Sun, N.N Shen and H.Y. Shum. Stereo matching using propagation belief, {\it TPAMI}. 2003.

\bibitem{c21}
M. Tao, J. Bai, P. Kohli, and S. Paris. SimpleFlow: A Non-iterative, Sublinear Optical Flow Algorithm, {\it Computer Graphics Forum, Eurographics}. 2012.

\bibitem{c9}
R. Achanta; A. Shaji; K. Smith; Aurelien Lucchi; P. Fua and S. Susstrunk, SLIC Superpixels compared to state of the art superpixel methods, {\it Discrete applied Mathematics.}, 2002.

\bibitem{c17}
S. Baker, D. Scharstein, J.P. Lewis, S. Roth, M.J. Black and R. Szeliski. A Database and Evaluation Methodology for Optical Flow, {\it International Journal Computer Vision}. 2013.

\bibitem{c23}
S. Hare, A. Saffari, and P.H.S. Torr, Struck: Structured Output Tracking with Kernels.  {\it International Conference on Computer Vision}. 2011.

\bibitem{c20}
T. Crivelli, P.-H. Conze, P. Robert, M. Fradet and P. Perez. Multi-step flow fusion: towards accurate and dense correpondence in long video shots, {\it British Conference Machine Vision}. 2012.

\bibitem{c7}
V. Lempitsky, S. Roth and C. Rother, Fusion Flow: Discrete-Continuos optimization for optical flow estimation, {\it Computer Vision and Pattern Recognition}, 2008.

\bibitem{c19}
W. Li, D. Cosker and M. Brown. An anchor patch based optimization framework for reducing optical flow drift in long image sequences, {\it Asian Conference on Computer Vision}. 2012.

\bibitem{c18}
Y. Boykov, M-P. Jolly. Interactive Graph Cuts for Optimal Boundary \& Region Segmentation of Objects in N-D images, {\it International Conference on Computer Vision}. 2013.

\bibitem{c16}
Y. Wu, J. Lim and M.-H. Yang. Online object tracking: A benchmark, {\it Computer Vision and Pattern Recognition}. 2013.

\end{thebibliography}