\begin{thebibliography}{99}

\bibitem{c1}
J. Malik and X. Ren, Learning a classification model for segmentation, {\it Computer Vision, International Conference}, 2003.

\bibitem{c2}
S. Boltz; F. Nielsen and S. Soatto, Earth mover distance on superpixels{\it International Conference on Image Processing}, 2010.

\bibitem{c3}
E. Boros; P. Hammer and G. Tavares, Preprocessing of unconstrained quadratic binary optimization {\it RUTCOR}, 2010

\bibitem{c4}
E. Boros and P. Hammer, Pseudo-boolean optimization{\it Discrete applied Mathematics.}, 2002

\bibitem{c5}
B. Horn and B. Schunck, Determining Optical Flow{\it Artificial Intelligence}, 1981

\bibitem{c6}
H. Ishikawa and P. Bouthemy, Multimodal estimation of discontinous optical flow using Markov random fields{\it TPAMI.}, 1993

\bibitem{c7}
V. Lempitsky, S. Roth and C. Rother, Fusion Flow: Discrete-Continuos optimization for optical flow estimation{\it Computer Vision and Pattern Recognition}, 2008

\bibitem{c8}
M. Reso and J. Jachalsky, Temporally Consistent Superpixels{\it International Conference Computer Vision.}, 2011

\bibitem{c9}
R. Achanta; A. Shaji; K. Smith; Aurelien Lucchi; P. Fua and S. Susstrunk SLIC Superpixels compared to state of the art superpixel methods{\it Discrete applied Mathematics.}, 2002

\bibitem{c10}
F. Perbet and A. Maki, Homogeneus superpixels from random walks{\it MVA.}, 2011

\bibitem{c11}
C. Xu and J.J. Corso. Evaluation of super-voxel methods for early video proccesing. {\it Computer Vision and Pattern Recognition}. 2012.

\bibitem{c12}
A. Shekhovtsov, I. Kovtun and V. Hlavac. Efficient MRF deformation model for non-rigid image matching. {\it Computer Vision and Pattern Recognition}. 2007.

\bibitem{c13}
J. Sun, N.N Shen and H.Y. Shum. Stereo matching using propagation belief. {\it TPAMI}. 2003.

\bibitem{c14}
C. Rother, V. Kolmogorov and A. Blake. Grabcut: Interactive foreground extraction using iterated graph cuts. {\it SIGGRAPH}. 2004.

\bibitem{c15}
L. Yang, Y. Guo, X. Wu and X. Wang. A new video segmentation approach: Grabcut in local window. {\it Soft Computing and Pattern Recognition}. 2011.

\bibitem{c16}
Y. Wu, J. Lim and M.-H. Yang. Online object tracking: A benchmark. {\it Computer Vision and Pattern Recognition}. 2013.

\bibitem{c17}
S. Baker, D. Scharstein, J.P. Lewis, S. Roth, M.J. Black and R. Szeliski. A Database and Evaluation Methodology for Optical Flow {\it International Journal Computer Vision}. 2013.

\bibitem{c18}
Y. Boykov, M-P. Jolly. Interactive Graph Cuts for Optimal Boundary \& Region Segmentation of Objects in N-D images {\it International Conference on Computer Vision}. 2013.

\bibitem{c19}
W. Li, D. Cosker and M. Brown. An anchor patch based optimization framework for reducing optical flow drift in long image sequences. {\it Asian Conference on Computer Vision}. 2012.

\bibitem{c20}
T. Crivelli, P.-H. Conze, P. Robert, M. Fradet and P. Perez. Multi-step flow fusion: towards accurate and dense correpondence in long video shots. {\it British Conference Machine Vision}. 2012.

\bibitem{c21}
M. Tao, J. Bai, P. Kohli, and S. Paris. SimpleFlow: A Non-iterative, Sublinear Optical Flow Algorithm. {\it Computer Graphics Forum, Eurographics}. 2012.


\end{thebibliography}