%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\usepackage{epsf,graphicx}
\usepackage{latexsym,amssymb}
\usepackage{setspace,cite}

\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\title{\LARGE \bf
Foreground segmentation in video by background tracking via guided superpixel flow.
}

\author{
Juan Manuel Perez Rua, Tomas Crivelli and Patrick Perez% <-this % stops a space
\thanks{This was supported by Technicolor R\&D}
\thanks{Juan Manuel Perez Rua  is with Technicolor R\&D,
        {\tt\small juanmanuel.perezrua@technicolor.com}}%
\thanks{Tomas Crivelli  is with Technicolor R\&D,
        {\tt\small tomas.crivelli@technicolor.com}}%
\thanks{Patrick Perez  is with Technicolor R\&D,
        {\tt\small patrick.perez@technicolor.com}}%
}
\begin{document}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{abstract}
\input{introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{core}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{99}

\bibitem{c1}
J. Malik and X. Ren, Learning a classification model for segmentation, {\it Computer Vision, International Conference}, 2003.

\bibitem{c2}
S. Boltz; F. Nielsen and S. Soatto, Earth mover distance on superpixels{\it International Conference on Image Processing}, 2010.

\bibitem{c3}
E. Boros; P. Hammer and G. Tavares, Preprocessing of unconstrained quadratic binary optimization {\it RUTCOR}, 2010

\bibitem{c4}
E. Boros and P. Hammer, Pseudo-boolean optimization{\it Discrete applied Mathematics.}, 2002

\bibitem{c5}
B. Horn and B. Schunck, Determining Optical Flow{\it Artificial Intelligence}, 1981

\bibitem{c6}
H. Ishikawa and P. Bouthemy, Multimodal estimation of discontinous optical flow using Markov random fields{\it TPAMI.}, 1993

\bibitem{c7}
V. Lempitsky, S. Roth and C. Rother, Fusion Flow: Discrete-Continuos optimization for optical flow estimation{\it Computer Vision and Pattern Recognition}, 2008

\bibitem{c8}
M. Reso and J. Jachalsky, Temporally Consistent Superpixels{\it International Conference Computer Vision.}, 2011

\bibitem{c9}
R. Achanta; A. Shaji; K. Smith; Aurelien Lucchi; P. Fua and S. Susstrunk SLIC Superpixels compared to state of the art superpixel methods{\it Discrete applied Mathematics.}, 2002

\bibitem{c10}
F. Perbet and A. Maki, Homogeneus superpixels from random walks{\it MVA.}, 2011

\bibitem{c11}
C. Xu and J.J. Corso. Evaluation of super-voxel methods for early video proccesing. {\it Computer Vision and Pattern Recognition}. 2012.

\bibitem{c12}
A. Shekhovtsov, I. Kovtun and V. Hlavac. Efficient MRF deformation model for non-rigid image matching. {\it Computer Vision and Pattern Recognition}. 2007.

\bibitem{c13}
J. Sun, N.N Shen and H.Y. Shum. Stereo matching using propagation belief. {\it TPAMI}. 2003.

\bibitem{c14}
C. Rother, V. Kolmogorov and A. Blake. Grabcut: Interactive foreground extraction using iterated graph cuts. {\it SIGGRAPH}. 2004.

\bibitem{c15}
L. Yang, Y. Guo, X. Wu and X. Wang. A new video segmentation approach: Grabcut in local window. {\it Soft Computing and Pattern Recognition}. 2011.

\end{thebibliography}

\end{document}
